The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-31 dit-paper_ieee.tex
changed one sentence

	We observe that the closer we are to the implicit deadline case ($CDF =
	0$), the fewer systems have a FPDIT. This is easily explained by the fact that
	a lower CDF means more idle instants for each task, and thus more opportunities
	for DITs to happen. Similarly, as all tasks must be synchronized for a DIT to
	happen, a higher number of tasks results in a decrease in FPDIT density.

>>>>

	We observe that when the $CDF$ tends to zero, few systems have a FPDIT.
	This is easily explained by the fact that
	a high CDF means more idle instants for each task, and thus more opportunities
	for DITs to happen. Similarly, as all tasks must be synchronized for a DIT to
	happen, a higher number of tasks results in a decrease in FPDIT density.
